Incentivizing Exploration with Unbiased History

### 2018-11-02 llevel.tex
C_0,N_0 => \estC, \estN
switch S to \NG

\section{Proofs of Section \ref{sec:llevel}}
\label{sec:llevel-details}
In this section, we design our $L$-level recommendation policy for $L > 3$. Similarly as Section \ref{sec:3level}, we first prove them in the case of 2 arms (Theorem \ref{thm:llevel} and Corollary \ref{cor:llevel}). We then extend them to the case of constant number of arms (Theorem \ref{thm:constarm}).

Now we start with the case of 2 arms. Our recommendation policy has $L$ levels and two types of groups: $G$-groups and $\Gamma$-groups. Each level has $S^2$ $G$-groups for $S = 2^{10}\log(T)$. Label the $G$-groups in the $l$-th level as $G_{l,u,v}$ for $u,v \in [S]$. Level $2$ to level $L$ also have $S^2$ $\Gamma$-groups. Label the $\Gamma$-groups in the $l$-th level as $\Gamma_{l,u,v}$ for $u,v \in [S]$. Each first-level group ($G_{1,u,v}$ for $u,v\in [S]$) has $T_1$ \ALGG of $\GdT$ rounds in parallel. For $l \geq 2$, there are $T_l$ agents in group $G_{l,u,v}$ and there are $T_l (S-1)$ agents in group $\Gamma_{l,u,v}$. We will pick $T_1,...,T_L$ in the proof of Theorem \ref{thm:llevel}.

Finally we define the info-graph. Agents in the first level only observe the history defined in the \ALGG run. For agents in group $G_{l,u,v}$ with $l\geq 2$, they observe all the history in the first $l-2$ levels (both $G$-groups and $\Gamma$-groups) and history in group $G_{l-1,v,w}$ for all $w \in [S]$. Agents in group $\Gamma_{l,u,v}$ observe the same history as agents in group $G_{l,u,v}$.

 \begin{comment}
\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \foreach \x in {0,3,6,9}
 {
 \filldraw[fill=orange!20!white]
 (\x+0,10)--(\x+0.8,10)--(\x+0.8,11)--(\x+0,11)--cycle;
 \filldraw[fill=orange!30!white]
 (\x+0.8,10)--(\x+2.8,10)--(\x+2.8,11)--(\x+0.8,11)--cycle;
 \filldraw[fill=purple!20!white]
 (\x+0,7.5)--(\x+0.8,7.5)--(\x+0.8,8.5)--(\x+0,8.5)--cycle;
 \filldraw[fill=purple!30!white]
 (\x+0.8,7.5)--(\x+2.8,7.5)--(\x+2.8,8.5)--(\x+0.8,8.5)--cycle;
 \filldraw[fill=green!20!white]
 (\x+0,5)--(\x+0.8,5)--(\x+0.8,6)--(\x+0,6)--cycle;
 \filldraw[fill=green!30!white]
 (\x+0.8,5)--(\x+2.8,5)--(\x+2.8,6)--(\x+0.8,6)--cycle;
 \filldraw[fill=blue!20!white]
 (\x+0,2.5)--(\x+0.8,2.5)--(\x+0.8,3.5)--(\x+0,3.5)--cycle;
 \filldraw[fill=blue!30!white]
 (\x+0.8,2.5)--(\x+2.8,2.5)--(\x+2.8,3.5)--(\x+0.8,3.5)--cycle;
 \filldraw[fill=red!20!white]
 (\x+0,0)--(\x+2.8,0)--(\x+2.8,1)--(\x+0,1)--cycle;
 \draw[dashed] (\x+0.4,0)--(\x+0.4,1); 
 \draw[dashed] (\x+0.8,0)--(\x+0.8,1); 
 \draw[dashed] (\x+1.2,0)--(\x+1.2,1); 
 \draw[dashed] (\x+1.6,0)--(\x+1.6,1);  
 \draw[dashed] (\x+2,0)--(\x+2,1);  
 \draw[dashed] (\x+2.4,0)--(\x+2.4,1);  
 \node at(\x+0.4,3){$T_{l-2}$};
 \node at(\x+1.8,3){$T_{l-2} (S-1)$};
 \node at(\x+0.4,5.5){$T_{l-1}$};
 \node at(\x+1.8,5.5){$T_{l-1} (S-1)$};
 \node at(\x+0.4,8){$T_l$};
 \node at(\x+1.8,8){$T_l (S-1)$};
 \node at(\x+0.4,10.5){$T_L$};
 \node at(\x+1.8,10.5){$T_L (S-1)$};
 \node at(\x+1.4,0.5){$T_1 \cdot \GdT$};
 }
\foreach \y in {0,2.5,5,7.5,10}
{
  \node at (12.5,\y+0.5){$\cdots$};
} 
\foreach \u in {1,2}
{
	\foreach \v in {1,2}
	{
	\pgfmathsetmacro{\x}{((\u-1)*2+(\v-1))*3};
	\pgfmathsetmacro{\xa}{((\u-1))*3};
	\pgfmathsetmacro{\xb}{(2+(\u-1))*3};
   \node at(\x+0.6,7){$G_{l,\u,\v}$};
   \node at(\x+0.6,4.5){$G_{l-1,\u,\v}$};
   \node at(\x+0.6,2){$G_{l-2,\u,\v}$};
   \node at(\x+2,7){$\Gamma_{l,\u,\v}$};
   \node at(\x+2,4.5){$\Gamma_{l-1,\u,\v}$};
   \node at(\x+2,2){$\Gamma_{l-2,\u,\v}$};
   %\draw[dashed] (\x+0.4,3.5)--(\xa+0.4,5);  
   %\draw[dashed] (\x+0.4,3.5)--(\xb+0.4,5);  
   %\draw[dashed] (\x+0.4,3.5)--(\xa+1.8,5);  
   %\draw[dashed] (\x+0.4,3.5)--(\xb+1.8,5);

@@

\begin{theorem}
\label{thm:llevel}
The $L$-level recommendation policy gets regret $O\left(T^{2^{L-1}/(2^L-1)} \log^2(T) \right)$ for $L \leq \log(\ln(T)/\log(S^4))$. In particular, if we pick $L = \log(\ln(T)/\log(S^4))$, the regret is $O(T^{1/2} polylog(T))$. 
\end{theorem}

\begin{proof}
Wlog we assume $\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both arms. We will set $T_l$'s later in the proof. Before that, we are only going to assume $T_l / T_{l-1} \geq S^4$ for $l=2,...,L-1$ and $T_1 \geq S^4$.

@@

For $a \in \{1,2\}$, define $\fdpN$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level. By Lemma \ref{lem:greedy}, we know $\GdP \leq \fdpN \leq \GdT$ For group $G_{1,u,v}$, define $W_1^{a,u,v}$ to be the event that the number of arm $a$ pulls in this group is between $\fdpN T_1- \GdT \sqrt{T_1\log(T)}$ and $\fdpN T_1 + \GdT \sqrt{T_1\log(T)}$. By Chernoff bound,
\[
\Pr[W_1^{a,u,v}] \geq 1-2\exp(-2\log(T)) \geq 1-2/T^2.
\]
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a,u,v}W_1^{a,u,v}$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{4S^2}{T^2}.
\]

@@

For $2\leq l \leq L-1$, $u\in [S]$ and each arm $a$, define $n^{l,u,a}$ to be the number of arm $a$ pulls in groups $G_{l,u,1},...,G_{l,u,S}$. Define $W_3^{l,u,a,high}$ as the event that $n^{l,u,a} \geq T_l$ implies the empirical mean of arm $a$ pulls in group $G_{l,u,1},...,G_{l,u,S}$ is at least $\mu_a + 1/\sqrt{n^{l,u,a}}$. Define $W_3^{l,u,a,low}$ as the event that $n^{l,u,a} \geq T_l$ implies the empirical mean of arm $a$ pulls in group $G_{l,u,1},...,G_{l,u,S}$ is at most $\mu_a - 1/\sqrt{n^{l,u,a}}$.

@@

Now consider $h_l$ to be any possible realized value of $H_l$. If fixing $H_l= h_l$ makes $n^{l,u,a}<T_l$, then $\Pr[W_3^{l,u,a,high} |H_l = h_l]=1$  If fixing $H_l = h_l$ makes $n^{l,u,a} \geq T_l$, by Berry-Esseen Theorem and $\mu_a \in [1/3,2/3]$, we have
\[
\Pr[W_3^{l,u,a,high}|H_l = h_l] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{T_l}} > 1/4.
\]
Similarly we also have
\[
\Pr[W_3^{l,u,a,low}|H_l = h_l]  > 1/4
\]
Since $W_3^{l,u,a,high}$ is independent with $W_3^{l,u,3-a,low}$ when fixing $H_l$, we have
\[
\Pr[ W_3^{l,u,a,high} \cap W_3^{l,u,3-a,low}|H_l = h_l]  > (1/4)^2 = 1/16.
\]
Now define $W_3^{l,a} = \bigcup_u (W_3^{l,u,a,high} \cap W_3^{l,u,3-a,low})$. Since  $(W_3^{l,u,a,high} \cap W_3^{l,u,3-a,low})$ are independent across different $u$'s when fixing $H_l=h_l$, we have
\[
\Pr[W_3^{l,a}|H_l= h_l] \geq 1- (1-1/16)^S \geq 1 - 1/T^2.
\]
Since this holds for all $h_l$'s, we have $\Pr[W_3^{l,a}] \geq 1-1/T^2$. Finally define $W_3 = \bigcap_{l,a} W_3^{l,a}$. By union bound, we have
\[
W_3 \geq 1 - 2L/T^2.
\]

@@

For first-level groups $G_{1,u,1},...,G_{1,u,S}$ and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in these groups pull arm $a$. Define $W_4^{u,a,high}$  to be the event that first $\fdpN T_1 S$ pulls of arm $a$ in the tape has empirical mean at least $\mu_a + 1/\sqrt{\fdpN T_1 S}$ and define $W_4^{u,a,low}$  to be the event that first $\fdpN T_1S$ pulls of arm $a$ in the tape has empirical mean at most $\mu_a - 1/\sqrt{\fdpN T_1S }$. By Berry-Esseen Theorem and $\mu_a \in [1/3,2/3]$, we have
\[
\Pr[W_4^{u,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{\fdpN T_1S}} > 1/4.
\]
The last inequality follows when $T$ is larger than some constant.
Similarly we also have 
\[
\Pr[W_4^{u,a,low}] > 1/4.
\]
Since $W_4^{u,a,high}$ is independent with $W_4^{u,3-a,low}$, we have
\[
\Pr[W_4^{u,a,high} \cap W_4^{u,3-a,low}] =\Pr[W_4^{u,a,high}] \cdot  \Pr[W_4^{u,3-a,low}]>(1/4)^2 = 1/16.
\]
Now define $W^{a}_4$ as $\bigcup_u (W_4^{u,a,high} \cap W_4^{u,3-a,low})$. Notice that $(W_4^{u,a,high} \cap W_4^{u,3-a,low})$ are independent across different $u$'s. So we have
\[
\Pr[W^{a}_4] \geq 1- (1-1/16)^S \geq 1 -1/T^2.
\]
Finally we define $W_4$ as $\bigcap_{a} W^{a}_4$. By union bound,
\[
\Pr[W_4] \geq 1- 2/T^2.
\]
\end{itemize}

@@

By event $W_1$, we know that in each first-level group, there are at least $\fdpN T_1- \GdT \sqrt{T_1\log(T)}$ pulls of arm $a$. We prove in the next claim that there are enough pulls of both arms in higher levels if $\mu_1-\mu_2$ is small enough. For notation convenience, we set $\varepsilon_0 = 1$, $\varepsilon_1 = \frac{1}{4\sqrt{\fdpN T_1S}} + \frac{1}{4\sqrt{\fdpN[3-a] T_1S}}$ and $\varepsilon_l = 1/(4\sqrt{T_lS})$ for $l \geq 2$.

\begin{claim}
\label{clm:l2_explore}
For any arm $a$ and $2\leq l \leq L$, if $\mu_1 - \mu_2 \leq \varepsilon_{l-1}$, then for any $u \in [S]$, there are at least $T_l$ pulls of arm $a$ in groups $G_{l,u,1},G_{l,u,2}, ... ,G_{l,u,S}$ and there are at least $T_lS(S-1)$ pulls of arm $a$ in the $l$-th level $\Gamma$-groups.
\end{claim}

\begin{proof}
We are going to show that for each $l$ and arm $a$ there exists $u_a$ such that agents in groups $G_{l,1,u_a},...,G_{l,S,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,S,u_a}$ all pull arm $a$. This suffices to prove the claim.

We prove the above via induction on $l$. %For notation convenience, define $\bar{\mu}^{l,u}_a$  to be the empirical mean of arm $a$ pulls in the history observed by agents in groups $G_{l,1,u},...,G_{l,S,u}$ and $\Gamma_{l,1,u},...,\Gamma_{l,S,u}$ (they observe the same history).
We start by the base case when $l=2$. For each arm $a$, $W_4$ implies there exists $u_a$ such that $W^{u_a,a,high}_4$ and $W^{u_a,3-a,low}_4$ happen. For an agent $t$  in groups $G_{2,1,u_a},...,G_{2,S,u_a}$ and $\Gamma_{2,1,u_a},...,\Gamma_{2,S,u_a}$.
$W_4^{u_a,a,high}$,  $W_1^{a,u_a,v}$ and $W_2$ together imply that 
\begin{align*}
\bar{\mu}_a ^t &\geq \mu_a + \left(\fdpN T_1S \cdot \frac{1}{\sqrt{\fdpN T_1S}} - \GdT \sqrt{T_1\log(T)} S\cdot \sqrt{\frac{3\log(T)}{ \GdT \sqrt{T_1\log(T)}S}} \right) \cdot \frac{1}{(\fdpN T_1+ \GdT \sqrt{T_1\log(T)})S} \\
&> \mu_a + \frac{1}{4\sqrt{\fdpN T_1S}}.
\end{align*}
The second last inequality holds when $T$ is larger than some constant.
Similarly, we also have
\[
\bar{\mu}_{3-a}^t< \mu_{3-a}   - \frac{1}{4\sqrt{\fdpN[3-a] T_1S}}.
\]
Then we have
\begin{align*}
\bar{\mu}^t_a - \bar{\mu}^t_{3-a} &> \mu_a - \mu_{3-a} + \frac{1}{4\sqrt{\fdpN T_1S}} + \frac{1}{4\sqrt{\fdpN[3-a] T_1S}}\\
&\geq -\varepsilon_1+ \frac{1}{4\sqrt{\fdpN T_1S}} + \frac{1}{4\sqrt{\fdpN[3-a] T_1S}}\\
&\geq \frac{1}{8\sqrt{\fdpN T_1S}} + \frac{1}{8\sqrt{\fdpN[3-a] T_1S}}.
\end{align*}
By Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &> \bar{\mu}^t_a - \bar{\mu}^t_{3-a} -  \frac{C_0}{\sqrt{\fdpN T_1S/2}} - \frac{C_0}{\sqrt{\fdpN[3-a] T_1S/2}}\\
&> \frac{1}{8\sqrt{\fdpN T_1S}} + \frac{1}{8\sqrt{\fdpN[3-a] T_1S}} -   \frac{C_0}{\sqrt{\fdpN T_1S/2}} - \frac{C_0}{\sqrt{\fdpN[3-a] T_1S/2}}\\
&>0.
\end{align*}
The last inequality holds since $C_0$ is a small enough constant defined in Assumption \ref{ass:embehave}. Therefore we know agents in groups $G_{2,1,u_a},...,G_{2,S,u_a}$ and $\Gamma_{2,1,u_a},...,\Gamma_{2,S,u_a}$ all pull arm $a$.

>>>>

\section{Proofs from Section \ref{sec:llevel}}
\label{sec:llevel-details}
In this section, we design our $L$-level recommendation policy for $L > 3$. Similarly as Section \ref{sec:3level}, we first prove them in the case of 2 arms (Theorem \ref{thm:llevel} and Corollary \ref{cor:llevel}). We then extend them to the case of constant number of arms (Theorem \ref{thm:constarm}).

Now we start with the case of 2 arms. Our recommendation policy has $L$ levels and two types of groups: $G$-groups and $\Gamma$-groups. Each level has $\NG^2$ $G$-groups for $\NG = 2^{10}\log(T)$. Label the $G$-groups in the $l$-th level as $G_{l,u,v}$ for $u,v \in [\NG]$. Level $2$ to level $L$ also have $\NG^2$ $\Gamma$-groups. Label the $\Gamma$-groups in the $l$-th level as $\Gamma_{l,u,v}$ for $u,v \in [\NG]$. Each first-level group ($G_{1,u,v}$ for $u,v\in [\NG]$) has $T_1$ \ALGG of $\GdT$ rounds in parallel. For $l \geq 2$, there are $T_l$ agents in group $G_{l,u,v}$ and there are $T_l (\NG-1)$ agents in group $\Gamma_{l,u,v}$. We will pick $T_1,...,T_L$ in the proof of Theorem \ref{thm:llevel}.

Finally we define the info-graph. Agents in the first level only observe the history defined in the \ALGG run. For agents in group $G_{l,u,v}$ with $l\geq 2$, they observe all the history in the first $l-2$ levels (both $G$-groups and $\Gamma$-groups) and history in group $G_{l-1,v,w}$ for all $w \in [\NG]$. Agents in group $\Gamma_{l,u,v}$ observe the same history as agents in group $G_{l,u,v}$.

 \begin{comment}
\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \foreach \x in {0,3,6,9}
 {
 \filldraw[fill=orange!20!white]
 (\x+0,10)--(\x+0.8,10)--(\x+0.8,11)--(\x+0,11)--cycle;
 \filldraw[fill=orange!30!white]
 (\x+0.8,10)--(\x+2.8,10)--(\x+2.8,11)--(\x+0.8,11)--cycle;
 \filldraw[fill=purple!20!white]
 (\x+0,7.5)--(\x+0.8,7.5)--(\x+0.8,8.5)--(\x+0,8.5)--cycle;
 \filldraw[fill=purple!30!white]
 (\x+0.8,7.5)--(\x+2.8,7.5)--(\x+2.8,8.5)--(\x+0.8,8.5)--cycle;
 \filldraw[fill=green!20!white]
 (\x+0,5)--(\x+0.8,5)--(\x+0.8,6)--(\x+0,6)--cycle;
 \filldraw[fill=green!30!white]
 (\x+0.8,5)--(\x+2.8,5)--(\x+2.8,6)--(\x+0.8,6)--cycle;
 \filldraw[fill=blue!20!white]
 (\x+0,2.5)--(\x+0.8,2.5)--(\x+0.8,3.5)--(\x+0,3.5)--cycle;
 \filldraw[fill=blue!30!white]
 (\x+0.8,2.5)--(\x+2.8,2.5)--(\x+2.8,3.5)--(\x+0.8,3.5)--cycle;
 \filldraw[fill=red!20!white]
 (\x+0,0)--(\x+2.8,0)--(\x+2.8,1)--(\x+0,1)--cycle;
 \draw[dashed] (\x+0.4,0)--(\x+0.4,1); 
 \draw[dashed] (\x+0.8,0)--(\x+0.8,1); 
 \draw[dashed] (\x+1.2,0)--(\x+1.2,1); 
 \draw[dashed] (\x+1.6,0)--(\x+1.6,1);  
 \draw[dashed] (\x+2,0)--(\x+2,1);  
 \draw[dashed] (\x+2.4,0)--(\x+2.4,1);  
 \node at(\x+0.4,3){$T_{l-2}$};
 \node at(\x+1.8,3){$T_{l-2} (\NG-1)$};
 \node at(\x+0.4,5.5){$T_{l-1}$};
 \node at(\x+1.8,5.5){$T_{l-1} (\NG-1)$};
 \node at(\x+0.4,8){$T_l$};
 \node at(\x+1.8,8){$T_l (\NG-1)$};
 \node at(\x+0.4,10.5){$T_L$};
 \node at(\x+1.8,10.5){$T_L (\NG-1)$};
 \node at(\x+1.4,0.5){$T_1 \cdot \GdT$};
 }
\foreach \y in {0,2.5,5,7.5,10}
{
  \node at (12.5,\y+0.5){$\cdots$};
} 
\foreach \u in {1,2}
{
	\foreach \v in {1,2}
	{
	\pgfmathsetmacro{\x}{((\u-1)*2+(\v-1))*3};
	\pgfmathsetmacro{\xa}{((\u-1))*3};
	\pgfmathsetmacro{\xb}{(2+(\u-1))*3};
   \node at(\x+0.6,7){$G_{l,\u,\v}$};
   \node at(\x+0.6,4.5){$G_{l-1,\u,\v}$};
   \node at(\x+0.6,2){$G_{l-2,\u,\v}$};
   \node at(\x+2,7){$\Gamma_{l,\u,\v}$};
   \node at(\x+2,4.5){$\Gamma_{l-1,\u,\v}$};
   \node at(\x+2,2){$\Gamma_{l-2,\u,\v}$};
   %\draw[dashed] (\x+0.4,3.5)--(\xa+0.4,5);  
   %\draw[dashed] (\x+0.4,3.5)--(\xb+0.4,5);  
   %\draw[dashed] (\x+0.4,3.5)--(\xa+1.8,5);  
   %\draw[dashed] (\x+0.4,3.5)--(\xb+1.8,5);

@@

\begin{theorem}
\label{thm:llevel}
The $L$-level recommendation policy gets regret $O\left(T^{2^{L-1}/(2^L-1)} \log^2(T) \right)$ for $L \leq \log(\ln(T)/\log(\NG^4))$. In particular, if we pick $L = \log(\ln(T)/\log(\NG^4))$, the regret is $O(T^{1/2} polylog(T))$. 
\end{theorem}

\begin{proof}
Wlog we assume $\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both arms. We will set $T_l$'s later in the proof. Before that, we are only going to assume $T_l / T_{l-1} \geq \NG^4$ for $l=2,...,L-1$ and $T_1 \geq \NG^4$.

@@

For $a \in \{1,2\}$, define $\fdpN$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level. By Lemma \ref{lem:greedy}, we know $\GdP \leq \fdpN \leq \GdT$ For group $G_{1,u,v}$, define $W_1^{a,u,v}$ to be the event that the number of arm $a$ pulls in this group is between $\fdpN T_1- \GdT \sqrt{T_1\log(T)}$ and $\fdpN T_1 + \GdT \sqrt{T_1\log(T)}$. By Chernoff bound,
\[
\Pr[W_1^{a,u,v}] \geq 1-2\exp(-2\log(T)) \geq 1-2/T^2.
\]
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a,u,v}W_1^{a,u,v}$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{4\NG^2}{T^2}.
\]

@@

For $2\leq l \leq L-1$, $u\in [\NG]$ and each arm $a$, define $n^{l,u,a}$ to be the number of arm $a$ pulls in groups $G_{l,u,1},...,G_{l,u,\NG}$. Define $W_3^{l,u,a,high}$ as the event that $n^{l,u,a} \geq T_l$ implies the empirical mean of arm $a$ pulls in group $G_{l,u,1},...,G_{l,u,\NG}$ is at least $\mu_a + 1/\sqrt{n^{l,u,a}}$. Define $W_3^{l,u,a,low}$ as the event that $n^{l,u,a} \geq T_l$ implies the empirical mean of arm $a$ pulls in group $G_{l,u,1},...,G_{l,u,\NG}$ is at most $\mu_a - 1/\sqrt{n^{l,u,a}}$.

@@

Now consider $h_l$ to be any possible realized value of $H_l$. If fixing $H_l= h_l$ makes $n^{l,u,a}<T_l$, then $\Pr[W_3^{l,u,a,high} |H_l = h_l]=1$  If fixing $H_l = h_l$ makes $n^{l,u,a} \geq T_l$, by Berry-Esseen Theorem and $\mu_a \in [1/3,2/3]$, we have
\[
\Pr[W_3^{l,u,a,high}|H_l = h_l] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{T_l}} > 1/4.
\]
Similarly we also have
\[
\Pr[W_3^{l,u,a,low}|H_l = h_l]  > 1/4
\]
Since $W_3^{l,u,a,high}$ is independent with $W_3^{l,u,3-a,low}$ when fixing $H_l$, we have
\[
\Pr[ W_3^{l,u,a,high} \cap W_3^{l,u,3-a,low}|H_l = h_l]  > (1/4)^2 = 1/16.
\]
Now define $W_3^{l,a} = \bigcup_u (W_3^{l,u,a,high} \cap W_3^{l,u,3-a,low})$. Since  $(W_3^{l,u,a,high} \cap W_3^{l,u,3-a,low})$ are independent across different $u$'s when fixing $H_l=h_l$, we have
\[
\Pr[W_3^{l,a}|H_l= h_l] \geq 1- (1-1/16)^\NG \geq 1 - 1/T^2.
\]
Since this holds for all $h_l$'s, we have $\Pr[W_3^{l,a}] \geq 1-1/T^2$. Finally define $W_3 = \bigcap_{l,a} W_3^{l,a}$. By union bound, we have
\[
W_3 \geq 1 - 2L/T^2.
\]

@@

For first-level groups $G_{1,u,1},...,G_{1,u,\NG}$ and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in these groups pull arm $a$. Define $W_4^{u,a,high}$  to be the event that first $\fdpN T_1 \NG$ pulls of arm $a$ in the tape has empirical mean at least $\mu_a + 1/\sqrt{\fdpN T_1 \NG}$ and define $W_4^{u,a,low}$  to be the event that first $\fdpN T_1\NG$ pulls of arm $a$ in the tape has empirical mean at most $\mu_a - 1/\sqrt{\fdpN T_1\NG }$. By Berry-Esseen Theorem and $\mu_a \in [1/3,2/3]$, we have
\[
\Pr[W_4^{u,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{\fdpN T_1\NG}} > 1/4.
\]
The last inequality follows when $T$ is larger than some constant.
Similarly we also have 
\[
\Pr[W_4^{u,a,low}] > 1/4.
\]
Since $W_4^{u,a,high}$ is independent with $W_4^{u,3-a,low}$, we have
\[
\Pr[W_4^{u,a,high} \cap W_4^{u,3-a,low}] =\Pr[W_4^{u,a,high}] \cdot  \Pr[W_4^{u,3-a,low}]>(1/4)^2 = 1/16.
\]
Now define $W^{a}_4$ as $\bigcup_u (W_4^{u,a,high} \cap W_4^{u,3-a,low})$. Notice that $(W_4^{u,a,high} \cap W_4^{u,3-a,low})$ are independent across different $u$'s. So we have
\[
\Pr[W^{a}_4] \geq 1- (1-1/16)^\NG \geq 1 -1/T^2.
\]
Finally we define $W_4$ as $\bigcap_{a} W^{a}_4$. By union bound,
\[
\Pr[W_4] \geq 1- 2/T^2.
\]
\end{itemize}

@@

By event $W_1$, we know that in each first-level group, there are at least $\fdpN T_1- \GdT \sqrt{T_1\log(T)}$ pulls of arm $a$. We prove in the next claim that there are enough pulls of both arms in higher levels if $\mu_1-\mu_2$ is small enough. For notation convenience, we set $\varepsilon_0 = 1$, $\varepsilon_1 = \frac{1}{4\sqrt{\fdpN T_1\NG}} + \frac{1}{4\sqrt{\fdpN[3-a] T_1\NG}}$ and $\varepsilon_l = 1/(4\sqrt{T_l\NG})$ for $l \geq 2$.

\begin{claim}
\label{clm:l2_explore}
For any arm $a$ and $2\leq l \leq L$, if $\mu_1 - \mu_2 \leq \varepsilon_{l-1}$, then for any $u \in [\NG]$, there are at least $T_l$ pulls of arm $a$ in groups $G_{l,u,1},G_{l,u,2}, ... ,G_{l,u,\NG}$ and there are at least $T_l\NG(\NG-1)$ pulls of arm $a$ in the $l$-th level $\Gamma$-groups.
\end{claim}

\begin{proof}
We are going to show that for each $l$ and arm $a$ there exists $u_a$ such that agents in groups $G_{l,1,u_a},...,G_{l,\NG,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,\NG,u_a}$ all pull arm $a$. This suffices to prove the claim.

We prove the above via induction on $l$. %For notation convenience, define $\bar{\mu}^{l,u}_a$  to be the empirical mean of arm $a$ pulls in the history observed by agents in groups $G_{l,1,u},...,G_{l,\NG,u}$ and $\Gamma_{l,1,u},...,\Gamma_{l,\NG,u}$ (they observe the same history).
We start by the base case when $l=2$. For each arm $a$, $W_4$ implies there exists $u_a$ such that $W^{u_a,a,high}_4$ and $W^{u_a,3-a,low}_4$ happen. For an agent $t$  in groups $G_{2,1,u_a},...,G_{2,\NG,u_a}$ and $\Gamma_{2,1,u_a},...,\Gamma_{2,\NG,u_a}$.
$W_4^{u_a,a,high}$,  $W_1^{a,u_a,v}$ and $W_2$ together imply that 
\begin{align*}
\bar{\mu}_a ^t &\geq \mu_a + \left(\fdpN T_1\NG \cdot \frac{1}{\sqrt{\fdpN T_1\NG}} - \GdT \sqrt{T_1\log(T)} \NG\cdot \sqrt{\frac{3\log(T)}{ \GdT \sqrt{T_1\log(T)}\NG}} \right) \cdot \frac{1}{(\fdpN T_1+ \GdT \sqrt{T_1\log(T)})\NG} \\
&> \mu_a + \frac{1}{4\sqrt{\fdpN T_1\NG}}.
\end{align*}
The second last inequality holds when $T$ is larger than some constant.
Similarly, we also have
\[
\bar{\mu}_{3-a}^t< \mu_{3-a}   - \frac{1}{4\sqrt{\fdpN[3-a] T_1\NG}}.
\]
Then we have
\begin{align*}
\bar{\mu}^t_a - \bar{\mu}^t_{3-a} &> \mu_a - \mu_{3-a} + \frac{1}{4\sqrt{\fdpN T_1\NG}} + \frac{1}{4\sqrt{\fdpN[3-a] T_1\NG}}\\
&\geq -\varepsilon_1+ \frac{1}{4\sqrt{\fdpN T_1\NG}} + \frac{1}{4\sqrt{\fdpN[3-a] T_1\NG}}\\
&\geq \frac{1}{8\sqrt{\fdpN T_1\NG}} + \frac{1}{8\sqrt{\fdpN[3-a] T_1\NG}}.
\end{align*}
By Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &> \bar{\mu}^t_a - \bar{\mu}^t_{3-a} -  \frac{\estC}{\sqrt{\fdpN T_1\NG/2}} - \frac{\estC}{\sqrt{\fdpN[3-a] T_1\NG/2}}\\
&> \frac{1}{8\sqrt{\fdpN T_1\NG}} + \frac{1}{8\sqrt{\fdpN[3-a] T_1\NG}} -   \frac{\estC}{\sqrt{\fdpN T_1\NG/2}} - \frac{\estC}{\sqrt{\fdpN[3-a] T_1\NG/2}}\\
&>0.
\end{align*}
The last inequality holds since $\estC$ is a small enough constant defined in Assumption \ref{ass:embehave}. Therefore we know agents in groups $G_{2,1,u_a},...,G_{2,\NG,u_a}$ and $\Gamma_{2,1,u_a},...,\Gamma_{2,\NG,u_a}$ all pull arm $a$.
